---
title: "RLadies demo"
author: "[Chloe Yap](https://github.com/cyap7)"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  epuRate::PCTG:
    toc: true
    number_sections: true
    code_folding: hide
knit: (function(inputFile, encoding) { 
          rmarkdown::render(inputFile,
                        encoding=encoding, 
                        output_file='mtcars1') })
---

# Set-up

## Libraries

```{r}

library(data.table)
library(DT)

library(tidyverse)
library(broom)
library(ggstatsplot)
library(ggrepel)
library(wesanderson)

```

## Directories

- use of filen variable to generalisable
- use of organised directories

```{r}

filen <- "mtcars1"

root_dir <- "~/Documents/GitHub/RLadies"
scripts_dir <- paste(root_dir, "/scripts", sep = "")
data_dir <- paste(root_dir, "/data", sep = "")
out_dir <- paste(root_dir, "/output", sep = "")

```

## Read-in data

- this is just the usual mtcars dataset being read in here
- prefer to use fread

```{r}

mtcars_dir <- paste(data_dir, "/", filen, ".txt", sep = "")
mtcars <- data.table::fread(mtcars_dir)
mtcars <- as.data.frame(mtcars)
DT::datatable(mtcars)

```

## Run common QC across analyses

- the `local = knitr::knit_global()` part is important, as I discovered last night ...

```{r}

str(mtcars)
source(paste(scripts_dir, "/common_qc.R", sep = ""), local = knitr::knit_global())

```

## Look at data

- I like DT::datatable() as you can interactively look through data tables 

```{r}

datatable(mtcars)

```

## Some sneaky bash

- 2 alternatives here

```{r}

system(paste("grep Merc ", mtcars_dir, sep = ""), intern = T)

```

```{sh}

grep Merc ~/Documents/GitHub/RLadies/data/mtcars1.txt

```

# Analysis

## Summarise data

- use of group_by() %>% dplyr::summarise()

```{r}

mtcars %>% group_by(Brand) %>% dplyr::summarise(
  n = n(),
  mpg_mean = mean(mpg),
  mpg_sd = sd(mpg),
)

```

## Use of pivot_wider() (used to be spread())

- eg. for each group (eg. Brand) want to get summary statistics of variable X (eg. mean mpg) split by another variable Y (eg. gear)
- **N.B. the mtcars dataset isn't exactly optimal for this**

```{r}

mtcars %>% group_by(Brand, gear) %>% 
  dplyr::summarise(mean_mpg = mean(mpg)) %>% 
  pivot_wider(., names_from = gear, values_from = mean_mpg) %>%
  datatable()

```

## Linear models with tabulated format

```{r}

tidy_df <- parameters::model_parameters(model = lm(mpg ~ gear + cyl, data = mtcars), ci = 0.95, verbose = FALSE) %>% 
  parameters::standardize_names(style = "broom")

tidy_coef <- mtcars %>% mutate(group = c(rep(1, 16), rep(2, 16))) %>% 
  group_by(group) %>% 
  do(model = tidy(lm(mpg ~ gear + cyl, data = .))) %>% unnest(model)

```

# Plots

## Boxplot 

### ggplot()

```{r}

mtcars %>% mutate(gear = as.factor(gear)) %>%
  ggplot(aes(x = gear, y = mpg, fill = gear)) +
  geom_violin(alpha = 0.8) +
  geom_point(colour = "gray50", alpha = 0.8) +
  theme_bw() +
  theme(legend.position = "none") +
  scale_fill_manual(values = wes_palette(name = "Zissou1", 4, type = "discrete")[c(1,3,4)], name = "")

ggsave(paste(out_dir, "/", filen, "_ggplot.png", sep = ""))

```

### ggrepel()

```{r}

mtcars %>% mutate(label = ifelse(mpg > 25, Make, "")) %>%
  mutate(gear = as.factor(gear)) %>%
  ggplot(aes(x = gear, y = mpg, fill = gear)) +
  geom_violin(alpha = 0.8) +
  geom_point(colour = "gray50", alpha = 0.8) +
  theme_bw() +
  theme(legend.position = "none") +
  scale_fill_manual(values = wes_palette(name = "Zissou1", 4, type = "discrete")[c(1,3,4)], name = "") +
  geom_label_repel(aes(x = gear, y = mpg, label = ifelse(label != "", label, "")), force = 20, size = 4, min.segment.length = 0)

ggsave(paste(out_dir, "/", filen, "_ggplot_ggrepel.png", sep = ""))
ggsave(paste(out_dir, "/", filen, "_ggplot_ggrepel.svg", sep = ""))

```

### ggstatsplot()

- https://indrajeetpatil.github.io/ggstatsplot/

```{r}

mtcars %>% mutate(label = ifelse(mpg > 25, Make, "")) %>%
  mutate(gear = as.factor(gear)) %>%
  ggbetweenstats(
    x     = gear,
    y     = mpg,
    title = "Distribution of mpg across gears"
  )

ggsave(paste(out_dir, "/", filen, "_ggstatsplot.png", sep = ""))
ggsave(paste(out_dir, "/", filen, "_ggstatsplot.svg", sep = ""))

```

## Linear model plot

### ggstatsplot()

```{r}

lm1 <- lm(mpg ~ gear + cyl, data = mtcars)
ggcoefstats(lm1)

```

## Scatterplot

```{r}

ggscatterstats(
  data  = mtcars,
  x     = mpg,
  y     = hp,
  xlab  = "mpg",
  ylab  = "hp",
  title = "mtcars: hp vs mph"
)

```


## Now go over to Inkscape to manipulate